%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.8]{geometry} % Reduce document margins

%----------------------------------------------------------------------------------------
% NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{\Huge{Beichen}} % Your first name
\familyname{Xu} % Your last name

% All information in this block is optional, comment out any lines you don't need
\address{44 Princes Gate}{London, UK, SW7 2QA}
\mobile{+44 0741 091 5752}
\email{xb223@ic.ac.uk}
\homepage{beichenxu.com}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
% SUMMARY SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%\section{Summary}
%Highly motivated and detail-oriented graduate student specializing in Machine Learning and Big Data with a strong foundation in Physics. Experienced in developing and training machine learning models, conducting data analysis, and visualizing complex datasets. Proficient in Python, PyTorch, TensorFlow, and statistical methods, with hands-on experience in high-performance computing environments. Adept at collaborating with cross-functional teams and communicating technical concepts effectively. Seeking a challenging data science position to leverage analytical skills and contribute to innovative projects.
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2023--2024}{MRes Machine Learning and Big Data in the Physical Sciences}{Imperial College London}{Department of Physics}{}{Skills and Modules: Time Series Analysis, Accelerated Data Processing, Field-Programmable Gate Arrays (FPGA), Machine Learning, Statistical Methods for Experimental Physics}
\cventry{2020--2023}{B.Sc. Physics}{University of Birmingham}{School of Physics and Astronomy}{First Class Honours}{Skills and Modules: Lagrangian and Hamiltonian Mechanics, Eigen Physics, Linear Algebra, Relativity, Quantum Mechenics, Statistics, Complex Analysis}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\subsection{Internships}

\cventry{2022}{Summer Intern}{\textsc{Kavli Institute of Cosmology Cambridge}}{Cambridge}{}{
\begin{itemize}
    \item Conducted research on machine learning-enhanced Bayesian inference, utilizing nested sampling to train cosmology data and masked aggressive flow for posterior generation of different parameters.
    \item Developed and trained machine learning models to enhance data analysis accuracy, and created visualizations such as 2D plots and GIFs to illustrate AI training processes.
    \item Contributed to the "margarine" Python package on GitHub by adding a new objective function, showcasing proficiency in computing tools like Linux, vim, vimteractive, ssh, tmux, tqdm, and TensorFlow,  and studied state of art Python packages like margarine and anesthetic.
    \item Collaborated closely with a PhD student, engaging in regular discussions to refine research approaches, resulting in improved methodology and outcomes.
    \item Participated in an academic club, enhancing technical knowledge and communication skills by reading and discussing cutting-edge research papers with colleagues.
\end{itemize}}

\cventry{2021}{Summer Intern}{\textsc{Purple Mountain Observatory}}{Nanjing}{}{
\begin{itemize}
    \item Analyzed Gamma Ray Burst (GRB) data to investigate their causes and mechanisms, utilizing Python for data fitting and analysis with a focus on Swift GRB data.
    \item Applied statistical methods to improve the accuracy of GRB parameter estimation, gaining proficiency in the iminuit library for minimization and error analysis.
    \item Conducted a comprehensive literature review on GRB phenomena, integrating new insights into the research process.
    \item Developed communication skills by writing detailed reports summarizing research progress and results, and delivering presentations to the research team.
    \item Improved organizational skills by managing data collection and analysis processes efficiently, ensuring timely completion of project tasks.
\end{itemize}}

%----------------------------------------------------------------------------------------
% PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Project Experience}

\subsection{Academic}

\cventry{2024}{MRes Project}{\textsc{Imperial College London}}{London}{}{
\begin{itemize}
    \item Simulated multi-source gravitational wave time-series data, and developed and trained WGAN models to analyze these signals.
    \item Utilized Imperial College London's HPC for model training and data visualization, employing tools such as PyTorch, PyTorch Lightning, and GetDist for development, training, and analysis.
    \item Debugged neural networks to enhance performance and accuracy, implementing techniques such as early stopping and adaptive training to optimize the training process.
    \item Participated in weekly group meetings with my supervisor and a PhD colleague to discuss project progress and troubleshoot challenges, fostering collaborative problem-solving and improving project outcomes.
\end{itemize}}


%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2018}{18th Award Program for Future Scientists -- Second Prize}
\cvitem{2019}{Physics Olympiad in Jiangsu Province, China -- First prize}

%----------------------------------------------------------------------------------------
% LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Chinese}{Native}{}
\cvitemwithcomment{English}{Intermediate}{Conversational fluency}

%----------------------------------------------------------------------------------------

\section{Publications}
\cvitem{1}{Xu, Beichen, Jun Su, and Weiguo Wang. "An expanding balloon: a small universe." \textit{Physics Education} 53.6 (2018): 065005.}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Anime \& Comics}{Hiking}
\cvlistdoubleitem{Reading}{Strategy Gaming}

%----------------------------------------------------------------------------------------

\end{document}
